### 2023-10-20 vesicle_code/docs/confinedMulti/response.tex

%%%%%%%%
\item Finally, this study is interesting and provides new insights.
  However, I advise authors to improve the quantitative part of their
  results (variation with Ca or confinement or something else, phase
  diagram...) to be more relevant for a journal such as Soft Matter. I
  am waiting the new manuscript.

\noindent
{\bf Response:} Agarwal and Biros
(\url{http://www.doi.org/10.1103/PhysRevFluids.5.013603})  recently
showed that when a vesicle is in a channel with strong confinement,
there are at most two different shapes a vesicle can take on for
different capillary numbers (see Figure 18a). They observe this for
confinement ratios as large as 0.7, and our examples have a confinement
ratio closer to 2 (stronger confinement). At such strong confinement, we
do not expect the capillary number to have an effect on the vesicle
  shape. To substantiate this claim, we consider a single multicomponent
  vesicle in an unconfined non-linear shear flow at various capillary
  numbers and reduced areas. The phase diagram (Figure~\ref{fig:Phase})
  shows that the multicomponent vesicle is more symmetric in shape than
  the single-component vesicle for a wide range of capillary numbers and
  reduced areas. Based on this, we speculate that a phase diagram with
  strong confinement would be less interesting than the single-component
  case, so we exclude a phase diagram with confinement.

We have also discussed this topic with a colleague who works on
experiments with red blood cells forming a single line along the
mid-plane as they pass through stenosis. His experiments show that the
shape of the red blood cell inside this confined stenosis is independent
over a range of capillary numbers. For this reason, we focus on the
relationships between between the vesicle shape, lubrication layer,
excess pressure, and asymmetry relative to the midline.

We have started examining the dependence of the vesicle symmetry on
other dimensionless parameters such as the confinement ratio and the
floppy-to-stiff ratio. This may give rise to different phenomena
and analyses that would distract from the focus of this work. Given the extra time it will take to
explore the phase diagram in these dimensionless parameters, we hope the referee would agree with us that these results would be better suited in a different manuscript which is what we have been working on now, using results and analyses summarized in this manuscript.
\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{phaseDiagram.pdf}
  \caption{\label{fig:Phase} \small A phase diagram of a single
  multicomponent vesicle in an unconfined nonlinear shear flow. The
  capillary number has no effect on the steady state shape of the
  vesicle.}
\end{figure}

### 2023-10-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
fixed spelling mistake
yny

Another difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. 
%The bottom of Figure~\ref{fig:lubricationComposite} shows the
%tank-treading velocities of four Lagrangian points. The inset shows the
%vesicle configuration in the closely-fitting part of the channel, the
%black dashed line is the center line of the channel, the marks are the
%four Lagrangian points, and the rounded arrow denotes the direction of
%rotation. 
\textcolor{blue}
{
To determine if a vesicle is tank-treading, we first calculate the
average, maximum, and minimum tangential velocities over all $N$
Lagrangian points when the vesicle's center of mass is in the interval
$[4,10]$. If the difference of the maximum and minimum tangential
velocities is within 15\% of the average tangential velocity, we
characterize the vesicle as tank-treading. These relative spreads are
plotted in the bottom row of Figure~\ref{fig:lubricationComposite}. The
average tangential velocities are $-1.00 \times 10^{-1}$ for the stiff
single-component vesicle, $3.31 \times 10^{-2}$ for the floppy
single-component vesicle, and $-8.48 \times 10^{-1}$ for the
multicomponent vesicle. The difference of the maximum and minimum
velocities relative to the average tangential velocities is $1.2\%$ for
the stiff single-component vesicle, $12\%$ for the multicomponent
vesicle, and over $300\%$ for the floppy single-component vesicle.
Therefore, we classify the stiff single-component and multicomponent
vesicles as tank treading, while the floppy single-component is not tank
treading.}
%The stiff single-component and multicomponent vesicles are
%clearly tank treading.
The direction and speed of the tank-treading depends on how much of the
vesicle membrane is exposed to positive shear (below the center line)
versus how much is exposed to negative shear (above the center
line)~\cite{kao-bir-mis2009}. The majority of the membrane of the stiff
single-component and multicomponent vesicles are below the center line,
and this results in a clockwise tank-treading behavior. In contrast, the
majority of the membrane of the floppy single-component vesicle is above
the center line, and the result is counterclockwise 
\textcolor{blue}{
rotation, but, again, large normal deformations are occuring along with
the rotation.
%}
%tank-treading. 
%\textcolor{blue}{
Finally, the stiff single-component vesicle tank treads faster than the
multicomponent cases since more of its membrane is located below the
center line.
}
%In addition, the tank-treading velocity can be correlated to the
%percentage of its membrane that is below the center line. 
%We note, however, that the floppy single-component vesicle is still
%undergoing deformations, so the tangential velocities have not converged
%to a fixed value.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Contraction} A multicomponent vesicle in the
contracting geometry}
In this section, we consider a vesicle passing through a channel that
slowly contracts 
\textcolor{blue}{
from a width of $6.5$ to $0.63$,
}
and then immediately opens back up to a channel 
\textcolor{blue}{
with width $6.5$. In dimensioned units, the width of the neck is
$2~\mu$m.
}
We first consider the effect of the initial lipid concentration when the
floppy and stiff regions each make up half of the vesicle membrane. In
Figure~\ref{fig:RA6leftRightRand}, snapshots of vesicles with reduced
area $\alpha = 0.5$ with different initial lipid distributions are
illustrated. The initial distributions are (a) random, (b) stiff in the
front and floppy in the back, and (c) floppy in the front and stiff in
the back. 
\textcolor{blue}{
As previously mentioned, the initial random lipid distributions are
sampled from the uniform distribution with the range $[0,1]$.}
The vesicle with the random initial lipid distribution quickly
phase separates into two floppy and two stiff regions. As seen in the
stenosis geometry, further phase separation is delayed until the vesicle
is no longer under strong confinement. The vesicle with the stiff region
at the front maintains its orientation. In contrast, the vesicle with
the floppy region on the front reorients the floppy region towards the
back of the vesicle. In summary, in all three cases, the vesicle is
orienting itself so that the stiff region passes through the
constriction before the floppy region. Therefore, in subsequent
simulations, we initialize the vesicle's lipid concentration so that the
floppy region is in the back and its stiff region is in the front. The
vesicle shapes develop regions with high curvature in the floppy region
when they first pass through the narrowest part of the geometry, but
once the strong confinement is abruptly removed, these regions of high
curvature are quickly smoothed.

>>>>

Another difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. 
%The bottom of Figure~\ref{fig:lubricationComposite} shows the
%tank-treading velocities of four Lagrangian points. The inset shows the
%vesicle configuration in the closely-fitting part of the channel, the
%black dashed line is the center line of the channel, the marks are the
%four Lagrangian points, and the rounded arrow denotes the direction of
%rotation.

\textcolor{blue}
{Here we described the criterion for determining if a vesicle is tank-treading: we first calculate the
average, maximum, and minimum tangential velocities over all $N$
Lagrangian points when the vesicle's center of mass is in the interval
$[4,10]$. If the difference of the maximum and minimum tangential
velocities is within 15\% of the average tangential velocity, we
characterize the vesicle as tank-treading. These relative spreads are
plotted in the bottom row of Figure~\ref{fig:lubricationComposite}. The
average tangential velocities are $-1.00 \times 10^{-1}$ for the stiff
single-component vesicle, $3.31 \times 10^{-2}$ for the floppy
single-component vesicle, and $-8.48 \times 10^{-1}$ for the
multicomponent vesicle. The difference of the maximum and minimum
velocities relative to the average tangential velocities is $1.2\%$ for
the stiff single-component vesicle, $12\%$ for the multicomponent
vesicle, and over $300\%$ for the floppy single-component vesicle.
Therefore, we classify the stiff single-component and multicomponent
vesicles as tank treading, while the floppy single-component is not tank
treading.}
%The stiff single-component and multicomponent vesicles are
%clearly tank treading.

The direction and speed of the tank-treading depends on how much of the
vesicle membrane is exposed to positive shear (below the center line)
versus how much is exposed to negative shear (above the center
line)~\cite{kao-bir-mis2009}. The majority of the membrane of the stiff
single-component and multicomponent vesicles are below the center line,
and this results in a clockwise tank-treading behavior. In contrast, the
majority of the membrane of the floppy single-component vesicle is above
the center line, and the result is counterclockwise 
\textcolor{blue}{
rotation, but, again, large normal deformations are occurring along with
the rotation.
%}
%tank-treading. 
%\textcolor{blue}{
Finally, the stiff single-component vesicle tank treads faster than the
multicomponent cases since more of its membrane is located below the
center line.
}
%In addition, the tank-treading velocity can be correlated to the
%percentage of its membrane that is below the center line. 
%We note, however, that the floppy single-component vesicle is still
%undergoing deformations, so the tangential velocities have not converged
%to a fixed value.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Contraction} A multicomponent vesicle in the
contracting geometry}
In this section, we consider a vesicle passing through a channel that
slowly contracts 
\textcolor{blue}{
from a width of $6.5$ to $0.63$,
}
and then immediately opens back up to a channel 
\textcolor{blue}{
with width $6.5$. In dimensional units, the width of the neck is
$2~\mu$m.
}
We first consider the effect of the initial lipid concentration when the
floppy and stiff regions each make up half of the vesicle membrane. In
Figure~\ref{fig:RA6leftRightRand}, snapshots of vesicles with reduced
area $\alpha = 0.5$ with different initial lipid distributions are
illustrated. The initial distributions are (a) random, (b) stiff in the
front and floppy in the back, and (c) floppy in the front and stiff in
the back. 
\textcolor{blue}{
As previously mentioned, the initial random lipid distributions are
sampled from the uniform distribution with the range $[0,1]$.}
The vesicle with the random initial lipid distribution quickly
phase separates into two floppy and two stiff regions. As seen in the
stenosis geometry, further phase separation is delayed until the vesicle
is no longer under strong confinement. The vesicle with the stiff region
at the front maintains its orientation. In contrast, the vesicle with
the floppy region on the front reorients the floppy region towards the
back of the vesicle. In summary, in all three cases, the vesicle is
orienting itself so that the stiff region passes through the
constriction before the floppy region. Therefore, in subsequent
simulations, we initialize the vesicle's lipid concentration so that the
floppy region is in the back and its stiff region is in the front. The
vesicle shapes develop regions with high curvature in the floppy region
when they first pass through the narrowest part of the geometry, but
once the strong confinement is abruptly removed, these regions of high
curvature are quickly smoothed.
